Transforming Trash as an Artistic Act

### 2016-01-08 chapter4_reduced.tex
adding missing points
Former-commit-id: e0bc8a55ecfaec1fb59d7c767d7a834a1bc15614

@@

% TODO refre
\begin{quote}
Take a newspaper. Take some scissors. Choose from this paper an article the length you want to make your poem. Cut out the article. Next carefully cut out each of the words that make up this article and put them all in a bag. Shake gently. Next take out each cutting one after the other. Copy conscientiously in the order in which they left the bag. The poem will resemble you. And there you are--an infinitely original author of       charming sensibility, even though unappreciated by the vulgar herd.
\end{quote}

@@

% TODO boxes and wooden cases
To hold notebooks together I made several small boxes from discarded card boxes. Notebooks are put inside of them.

@@

Giving name is another hard topic for me. However point out the story behind the notebooks and properties of it. These nanes gives clues about how they are combined what they represent, defines the aspects of them. Name of the paper can be related with this place and related with the meaning. These names captures the memory of notebooks. However for one serie i barrowed the idea of nonsenseword generation from the kurt. similar to the the production of the nonsense word merz I decided to name some of the notebooks a nonsense word. There are notebook series that have a name. Here are the name of notebooks and their story:

\textbf{Puzzle.} Papers inside of the notebooks are cut out from very big and long banner (see figure \ref{fig:Banner_1}). Every piece is a part of bigger banner. Pages of paper is similar to the pieces of puzzle. All of them are composes the banner. However they are cut out and give away combining them is not possible but the image of the original one can be viewed on the website.

@@

\textbf{Reunion.} These notebook's pages are collected from restaurant "Varuna Gezgin". We go there to meet some friends after long time. One of them is coming from Australia, the other one is coming from Norway. They are my friends from the university. We united again at varuna gezgin. The place also interesting story. It is a place of travelers. It supports them. and the decoration of that place contains a lot of items collected from different sides of the world. The concept of the place and our meeting perfectly matched. I'm collecting the paper that are under the plates. When we are leaving this place, I ask the guy at the desk, I am making small notebooks and is it possible to exhibit there. I said that is it possible to give them to people. Firstly he asked me that selling them but I said no they are free and part of my thesis project. and later he offered me there are a lot of unused papers. I can give you. they are not used and waiting to be recycling. I took some of the papers, and that papers are part the sheets of these papers.

Same exist for the paper actually, they seperated and by the action making notebooks they are also reunited again.

\textbf{Second hand} It can be thought that these notebooks are second hand objects. Used by someone else and still appropriate for reusing.

\textbf{Dada}

>>>>

% I'm collecting the paper that are under the plates. When we are leaving this place, I ask the cashier at the desk that \quotes{I am making small notebooks and is it possible to exhibit there?} I asked that is it possible to give them to people. Firstly he asked me that did I sell them or not but I said \quotes{no they are free and part of my thesis project.} After that he offered me to give e are a lot of unused papers. I can give you. they are not used and waiting to be recycling. I took some of the papers, and that papers are part the sheets of these papers.

@@

\begin{quote}
Take a newspaper. Take some scissors. Choose from this paper an article the length you want to make your poem. Cut out the article. Next carefully cut out each of the words that make up this article and put them all in a bag. Shake gently. Next take out each cutting one after the other. Copy conscientiously in the order in which they left the bag. The poem will resemble you. And there you are--an infinitely original author of       charming sensibility, even though unappreciated by the vulgar herd.
\end{quote}

@@

% TODO boxes and wooden cases
To hold notebooks together I made several small boxes from discarded card boxes. Notebooks were put inside of them.

@@

Giving name is another hard topic for me. However point out the story behind the notebooks and properties of it. These names gives clues about how they are combined what they represent, defines the aspects of them. Name of the paper can be related with this place and related with the meaning. These names captures the memory of notebooks. However for one series I borrowed the idea of nonsense word generation from the Kurt Schwitters. Similar to the the production of the nonsense word merz I decided to name some of the notebooks a nonsense word. There are notebook series that have a name. Here are the name of notebooks and their story:

\textbf{Puzzle.} Papers inside of these notebooks are cut out from very big and long banner (see figure \ref{fig:Banner_1}). Every piece is a part of bigger banner. Pages of paper is similar to the pieces of puzzle. All of them are composes the banner. However they are cut out and give away combining them is not possible but the image of the original one can be viewed on the website.

@@

\textbf{Reunion.} These notebook's pages are collected from restaurant Varuna Gezgin, in Ankara. We went there to meet some friends after long time. One of them was coming from Australia, the other one was coming from Norway. They were my friends from the university. We united again at this restaurant. The place has also similar story. Their founders and workers travel around the world. It is a popular restaurant of travelers. The decoration of that place contains a lot of items collected from different sides of the world. The concept of the place and our meeting perfectly matched. Same exist for the papers actually, they are separated from big paper rolls in the factory and by the action making notebooks they are also reunited again. These notebooks represent my memory about the place.

\textbf{Secondhand.} It can be thought that these notebooks are second hand objects. Used by someone else and still appropriate for reusing.

% TODO burada bir isim uydurmak gerekli.
\textbf{Dada.} For some of the notebooks it is not obvious to name them. At this point approach of Kurt Schwitters provide me a way. He created his frequently used word \quotes{Merz} from an advertisement. It is a nonsense word and used it most of his works. I followed what he did and generated a word from a paper. I use this word for the ones the story of them are not obvious and significant.

### 2016-01-08 chapter5.tex
Reorganization.
Former-commit-id: 1502aeed78b3566ee9739270b736389b7fc1099d
adding missing points
Former-commit-id: e0bc8a55ecfaec1fb59d7c767d7a834a1bc15614

Inseparable part of our activities.
Trash is everywhere. Part of our activities. Rubbish as an object state is not static. Its value, usage may vary according to the people. Artistic intentions are aimed to transform the material. Whatever the reason that people are discarding things there must be other type of action that can be able to reverse it. Aimed to create new possibilities from trash.

% This thesis forms the basic principles and approaches in the act of transformation. This research provides a framework to look at trash differently.

% This thesis work attempts to understand the transformation of trash through the artistic practices. The usage of materials in these works provide audience new interpretation of the material.

% Through the analysis of selected works metadologies, approaches, placement trash, positing of trash ...  show that trash is fluid, and value indeterminate, and are often determined by context and personal subjectivities.

@@

%
%
\textbf{Evolution, Critics} During the process I have also generated lots of trashed papers. Cutting and pasting things also leave unused items. I do not know what to do with them. It is hard to use all of them. Saved for later use. On the other hand being aware of this transformation act is very tiny part of the big picture. I can say that my trash is reduced but is it same for the other people. Hard to collect all of them. 
There is also discard is being generated during the production process of papers. How to use them? Need to find a way because varda uses her discarded item inside of the film. Always(or in every processes) new discard items are generated.

%
%
\textbf{Future Works.} Web site will expand in time. New notebooks from different papers (in terms of location, meaning, usage purpose)

>>>>

% The need to the item is ended up and it is least profitable to save it. Now it is considered as excess.

% Toplama mekanları: Yollar, Bilkent labı. Sabahleyin geçtiğim yollarda genelde öğrencilerin bıraktıları simit pohaça gibi şeylerin paketleri bulunmakta. Bilkent labaratuvarı, Restraurants, Pazar yeri, Kendi çalıştığım ofis,

Trash is everywhere and produced every time. It is inseparable part of our activities. Rubbish as an object state is not static. Its value, usage might vary according to the people. Artistic intentions are aimed to transform the material. Whatever the reason that people are discarding things there must be other type of action that can be able to reverse it. Aimed to create new possibilities from trash.

This thesis forms the basic principles and approaches in the act of transformation. This research provides a framework to look at trash differently.

This thesis work attempts to understand the transformation of trash through the artistic practices. The usage of materials in these works provide audience new interpretation of the material. 
Through the analysis of selected works methodologies, approaches, placement trash, positing of trash ...  show that trash is fluid, and value indeterminate, and are often determined by context and personal subjectivities.

@@

%
%
During the process I have also generated lots of trashed papers. Cutting and pasting things also leave unused items. I do not know what to do with them. It is hard to use all of them. Saved for later use. On the other hand being aware of this transformation act is very tiny part of the big picture. I can say that my trash is reduced but is it same for the other people. Hard to collect all of them. There is also discard is being generated during the production process of papers. How to use them? Need to find a way because varda uses her discarded item inside of the film. Always(or in every processes) new discard items are generated.

%
%
Web site will expand in time. New notebooks from different papers (in terms of location, meaning, usage purpose)
